set3
========================================================

Loading ggplot and data

```{r Loading ggplot and data}
library(ggplot2); data(diamonds)
summary(diamonds)

```

Number of observations in data set
```{r Number of observations in data set}
dim(diamonds)[1]
```
Number of variables
```{r Number of variables}
dim(diamonds)[2]
```
Number of ordered factors
```{r Number of ordered factors}
str(diamonds)
```
Create a histogram of the price of
all the diamonds in the diamond data set.
```{r histogram of diamonds price}
qplot(x =price, data = diamonds, binwidth = 10) + 
  scale_x_continuous(limits = c(300, 19000), breaks = seq(0,  19000, 1000))
```
Exploring the largest peak in price
```{r Exploring the largest peak in price}
qplot(x =price, data = diamonds, binwidth = 10) + 
  scale_x_continuous(limits = c(500, 2000)) 
ggsave("diamonds.peak.png")
```
Diamond prices by cut histogram
```{r Diamond prices by cut histogram}
qplot(x =price, data = diamonds, binwidth = 10) + 
  scale_x_continuous(limits = c(300, 19000), breaks = seq(0,  19000, 1000)) +
  facet_wrap(~cut, 1)
```
Diamond prices by cut frequency polygon
```{r Diamond prices by cut frequency polygon}
qplot(x=price, data=diamonds, binwidth=40, geom='freqpoly', color=cut, xlim=c(200, 19000))
```
Cuts with the highest, lowest priced diamond
```{r Cuts with the highest priced diamond}
by(diamonds$price, diamonds$cut, max)
by(diamonds$price, diamonds$cut, min)
```
Diamond prices by cut histogram with no fixed y
```{r Diamond prices by cut histogram with no fixed y}
qplot(x =price, data = diamonds, binwidth = 50, color = I("black"), fill = I("#099DD9")) + 
  scale_x_continuous(limits = c(300, 19000), breaks = seq(0,  19000, 1000)) +
  facet_wrap(~cut,ncol = 1, scale = "free_y")
```
Price/carat histogram
```{r Price/carat histogram}
qplot(x = price / carat, data = diamonds,  binwidth = 0.005, color = I("black"), fill = I("#099DD9")) + facet_wrap(~cut,ncol = 1, scale = "free_y") + scale_x_log10()
```
Boxplots by cut, color, clarity
```{r Boxplots by cut, color, clarity}
qplot(x = cut, y = price, data = diamonds, geom = "boxplot") 
by(diamonds$price, diamonds$cut, summary)
qplot(x = color, y = price, data = diamonds, geom = "boxplot") 
by(diamonds$price, diamonds$color, IQR)
qplot(x = clarity, y = price, data = diamonds, geom = "boxplot") 
IQR(subset)
?diamonds
```
Price/carat boxplot across colors
```{r}
qplot(x = color, y = price / carat, data = diamonds, geom = "boxplot", color = cut)
```
Carat frequency polygon
```{r Carat frequency polygon}
qplot(x = carat, data = diamonds, geom = "freqpoly", binwidth = 0.02) + scale_x_discrete(breaks = seq(0, 5.01, 0.04))
summary(diamonds$carat)
table(diamonds$carat)[table(diamonds$carat)>2000] 
```
Subsetting the best and worst diamonds and plotting
```{r Subsetting the best and worst diamonds and plotting}
rock <- subset(diamonds,cut == "Fair" & color == "J" & clarity == "I1")
ideal <- subset(diamonds,cut == "Ideal" & color == "D" & clarity == "IF")
p1 <- qplot(x=carat, y = price/carat, data = rock) + scale_x_continuous(lim=c(0,5.5)) + scale_y_continuous(lim=c(0,5000)) + labs( title="Low Quality Diamonds" )
p2 <- qplot(x=carat, y = price/carat, data = ideal) + scale_x_continuous(lim=c(0,1.2)) + scale_y_continuous(lim=c(0,18000)) + labs(title = "High Quality Diamonds")
library(gridExtra)
grid.arrange(p1,p2, ncol =1)
```


